---
title: "MNIST"
author: "Jiyi Jiang"
date: "June 11, 2015"
output: html_document
---

```{r}
```{r}
# Load the MNIST digit recognition dataset into R
# http://yann.lecun.com/exdb/mnist/
# assume you have all 4 files and gunzip'd them
# creates train$n, train$x, train$y  and test$n, test$x, test$y
# e.g. train$x is a 60000 x 784 matrix, each row is one digit (28x28)
# call:  show_digit(train$x[5,])   to see a digit.
# brendan o'connor - gist.github.com/39760 - anyall.org
setwd("C:\Users\sumloaner\Downloads")

load_mnist <- function() {
  load_image_file <- function(filename) {
    ret = list()
    f = file(filename,'rb')
    readBin(f,'integer',n=1,size=4,endian='big')
    ret$n = readBin(f,'integer',n=1,size=4,endian='big')
    nrow = readBin(f,'integer',n=1,size=4,endian='big')
    ncol = readBin(f,'integer',n=1,size=4,endian='big')
    x = readBin(f,'integer',n=ret$n*nrow*ncol,size=1,signed=F)
    ret$x = matrix(x, ncol=nrow*ncol, byrow=T)
    close(f)
    ret
  }
  load_label_file <- function(filename) {
    f = file(filename,'rb')
    readBin(f,'integer',n=1,size=4,endian='big')
    n = readBin(f,'integer',n=1,size=4,endian='big')
    y = readBin(f,'integer',n=n,size=1,signed=F)
    close(f)
    y
  }
  train <<- load_image_file('train-images-idx3-ubyte')
  test <<- load_image_file('t10k-images-idx3-ubyte')
  
  train$y <<- load_label_file('train-labels-idx1-ubyte')
  test$y <<- load_label_file('t10k-labels-idx1-ubyte')  
}


show_digit <- function(arr784, col=gray(12:1/12), ...) {
  image(matrix(arr784, nrow=28)[,28:1], col=col, ...)
}

load_mnist()
train$n
```

```{R}
#Good one
#USE tsne
set.seed(600003)
X=train$x

# create an index vector
ind <- sample(nrow(X),size=2000,replace=FALSE)
labels <- train$y[ind]

try=X[ind,]# number of random rows of 60000.
library(tsne)
result=tsne(try, initial_config = NULL, k = 2, initial_dims = 30, perplexity = 30, max_iter = 1000, min_cost = 0, epoch_callback = NULL, whiten = TRUE, epoch=100)
cc1=gsub("1","gold",labels)
cc2=gsub("0","darkgreen",CC1)
plot(result,col=cc2)

#USE TSNE
set.seed(600007)
X=train$x

# create an index vector
ind <- sample(nrow(X),size=2000,replace=FALSE)
labels <- train$y[ind]

try=X[ind,]# number of random rows of 60000.
library(tsne)
result=tsne(try, initial_config = NULL, k = 2, initial_dims = 30, perplexity = 25, max_iter = 1000, min_cost = 0, epoch_callback = NULL, whiten = TRUE, epoch=100)
cc1=gsub("1","gold",labels)
cc2=gsub("0","darkgreen",cc1)
plot(result,col=cc2)

#EVEN BETTER
#USE tsne
set.seed(600007)
X=train$x

# create an index vector
ind <- sample(nrow(X),size=2000,replace=FALSE)
labels <- train$y[ind]

try=X[ind,]# number of random rows of 60000.
library(tsne)
result=tsne(try, initial_config = NULL, k = 2, initial_dims = 22, perplexity = 20, max_iter = 1000, min_cost = 0, epoch_callback = NULL, whiten = TRUE, epoch=100)
cc1=gsub("1","gold",labels)
cc2=gsub("0","darkgreen",cc1)
plot(result,col=cc2)

#
#USE TSNE
set.seed(600007)
X=train$x

# create an index vector
ind <- sample(nrow(X),size=2000,replace=FALSE)
labels <- train$y[ind]

try=X[ind,]# number of random rows of 60000.
library(tsne)
result=tsne(try, initial_config = NULL, k = 2, initial_dims = 30, perplexity = 12, max_iter = 1000, min_cost = 0.05, epoch_callback = NULL, whiten = TRUE, epoch=100)
cc1=gsub("1","gold",labels)
cc2=gsub("0","darkgreen",cc1)
plot(result,col=cc2)

#initial 20, perp 30
set.seed(600014)
X=train$x
# create an index vector
ind <- sample(nrow(X),size=2000,replace=FALSE)
labels <- train$y[ind]

try=X[ind,]# number of random rows of 60000.
library(tsne)
result=tsne(try, initial_config = NULL, k = 2, initial_dims = 20, perplexity = 30, max_iter = 1000, min_cost = 0, epoch_callback = NULL, whiten = TRUE, epoch=100)
cc1=gsub("1","gold",labels)
cc2=gsub("0","darkgreen",cc1)
plot(result,col=cc2)

#initial 10, perp30
set.seed(600014)
X=train$x
# create an index vector
ind <- sample(nrow(X),size=2000,replace=FALSE)
labels <- train$y[ind]

try=X[ind,]# number of random rows of 60000.
library(tsne)
result=tsne(try, initial_config = NULL, k = 2, initial_dims = 10, perplexity = 27, max_iter = 1000, min_cost = 0.01, epoch_callback = NULL, whiten = TRUE, epoch=100)
cc1=gsub("1","gold",labels)
cc2=gsub("0","darkgreen",cc1)
plot(result,col=cc2)

#USE Rtsne
set.seed(620251)
ind <- sample(nrow(train$x),size=6000,replace=FALSE)
labels <- train$y[ind]
Rtsne_input=train$x[ind,]# number of random rows of 60000.
library(Rtsne)
Rtsne_result=Rtsne(Rtsne_input, dims = 2, initial_dims = 20, perplexity = 20,
        theta = 0.1, check_duplicates = TRUE, pca = TRUE, max_iter = 1000,
        verbose = FALSE, is_distance = FALSE,)
cc1=gsub("1","gold",labels)
cc2=gsub("0","darkgreen",cc1)
plot(Rtsne_result$Y,col=cc2)

#SVD for MNIST
---
title: "SVD"
author: "Jiyi Jiang"
date: "June 24, 2015"
output: html_document
---


```{r}
R156=train$x[156,]
M156=matrix(R156,28,28,)
image(M156)
M156_svd=svd(M156)

d <- M156_svd$d
u <- M156_svd$u
v <- M156_svd$v

for (i in c(3, 4, 5, 15, 20, 25))
{
    M156.compressed <- u[,1:i] %*% diag(d[1:i]) %*% t(v[,1:i])
    image(M156.compressed)
}


#show_digit(train$x[1,])
ind <- sample(nrow(X),size=2000,replace=FALSE)
show_digit(train$x[159,])
 
R156 <- train$x[159,]
M156 <- matrix(R156, nrow=28)[,28:1]
image(M156,col=gray(12:1/12))
M156_svd <- svd(M156)
d <- M156_svd$d
u <- M156_svd$u
v <- M156_svd$v

for (i in c(8))
{
    M156.compressed <- u[,1:i] %*% diag(d[1:i]) %*% t(v[,1:i])
    image(M156.compressed,col=gray(12:1/12))
}

x=abs(M156- M156.compressed)
image(x, col=gray(12:1/12))
```

Pre-processing MNIST

```{r, echo=FALSE}
#show_digit(train$x[1,])
ind <- sample(nrow(X),size=2,replace=FALSE)
show_digit(train$x[1:2,])
 
R156 <- c(train$x[ind,])
M156 <- matrix(R156, nrow=28)[,28:1]
image(M156,col=gray(12:1/12))
M156_svd <- svd(M156)
d <- M156_svd$d
u <- M156_svd$u
v <- M156_svd$v

for (i in c(8))
{
    M156.compressed <- u[,1:i] %*% diag(d[1:i]) %*% t(v[,1:i])
    image(M156.compressed,col=gray(12:1/12))
}

x=abs(M156- M156.compressed)
image(x, col=gray(12:1/12))
```





